\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-23 doc/flexiblesusy-paper.tex
added a footnote to section 5 where the NMSSM/MSSM corrections issue is dicussed.

\fs allows the user to add leading two-loop contributions to the
CP-even Higgs tadpoles and self-energies.  For MSSM-like models (with
two CP-even Higgs bosons, one CP-odd Higgs boson, one neutral
Goldstone boson) routines dor caluclating these corrections will be
generated by setting \code{UseHiggs2LoopMSSM = True} in the model file
and by defining the effective $\mu$-term \code{EffectiveMu = \\[Mu]}.
This will add the zero-momentum corrections of the order $O(y_t^4 +
y_b^2 y_t^2 + y_b^4)$, $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$,
$O(y_\tau^4)$ from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}.
For NMSSM-like models (with three CP-even Higgs bosons, two CP-odd
Higgs bosons, one neutral Goldstone boson) the two-loop contributions
are generated by setting \code{UseHiggs2LoopNMSSM = True} and by
defining the effective $\mu$-term like \code{EffectiveMu = \\[Lambda]
  vS / Sqrt[2]}, for example.  This will add the zero-momentum
corrections of the order $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ from
\cite{Degrassi:2009yq} and also the MSSM contributions of the order
$O(y_\tau^4)$, $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ as well
\cite{Brignole:2001jy,Dedes:2003km} which only represent a partial
correction for that order in the NMSSM, but can be a good approximation
when singlet mixing is very small.

@@

  When two loop corrections have been enabled in the SLHA
  file by setting entry 4 of the FlexibleSUSY block to 2 the user may
  also select individual corrections. Entries 9,10,11 and 12,
  correspond to two loop corrections of order $\oatas$, $\oabas$,
  $\oatplusabsq$ and $\oatauq$ respectively and will be disabled when
  the corresponding entry is set to zero. In this way, for example, in
  the NMSSM the user may decide not to use the partial corrections at
  order $\oatplusabsq$ and $\oatauq$, all of which have
  only been computed in the MSSM.

>>>>

\fs allows the user to add leading two-loop contributions to the
CP-even Higgs tadpoles and self-energies.  For MSSM-like models (with
two CP-even Higgs bosons, one CP-odd Higgs boson, one neutral
Goldstone boson) routines dor caluclating these corrections will be
generated by setting \code{UseHiggs2LoopMSSM = True} in the model file
and by defining the effective $\mu$-term \code{EffectiveMu = \\[Mu]}.
This will add the zero-momentum corrections of the order $O(y_t^4 +
y_b^2 y_t^2 + y_b^4)$, $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$,
$O(y_\tau^4)$ from
\cite{Degrassi:2001yf,Brignole:2001jy,Dedes:2002dy,Brignole:2002bz,Dedes:2003km}.
For NMSSM-like models (with three CP-even Higgs bosons, two CP-odd
Higgs bosons, one neutral Goldstone boson) the two-loop contributions
are generated by setting \code{UseHiggs2LoopNMSSM = True} and by
defining the effective $\mu$-term like \code{EffectiveMu = \\[Lambda]
  vS / Sqrt[2]}, for example.  This will add the zero-momentum
corrections of the order $O(y_t^2 g_3^2)$, $O(y_b^2 g_3^2)$ from
\cite{Degrassi:2009yq} and also the MSSM contributions of the order
$O(y_\tau^4)$, $O(y_t^4 + y_t^2 y_b^2 + y_b^4)$ as well
\cite{Brignole:2001jy,Dedes:2003km} which only represent a partial
correction for that order in the NMSSM, but can be a good approximation
when singlet mixing is very small\footnote{These corrections may be disabled in the SLHA file, as described in section \secref{sec:PoleMasses}.}.

@@

  When two loop corrections have been enabled in the SLHA
  file by setting entry $4$ of the FlexibleSUSY block to $2$ the user may
  also select individual corrections. Entries $9$,$10$,$11$ and $12$,
  correspond to two loop corrections of order $\oatas$, $\oabas$,
  $\oatplusabsq$ and $\oatauq$ respectively and will be disabled when
  the corresponding entry is set to zero. In this way, for example, in
  the NMSSM the user may decide not to use the partial corrections at
  order $\oatplusabsq$ and $\oatauq$, all of which have
  only been computed in the MSSM.
